Time series plots

### 2021-09-22 src/old/LAs_Clusters.Rmd
tidy up

aux <- multinom(cluster.up ~ 
                  #pop16_64 + # non sign, while pop is
                  pop +
                  #pop.dens + 
                  job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                  distMet + distLondon + south +
                  managers + tech + skilled + prof + admin + caring + plant +
                  earnings + I(total.busi/pop) + nvq4 +
                  I(LAD.tests.am20/pop) + # non sensitive to addition of other tests pm
                  virgin
                , data = data, 
                trace = F) # to avoid messages

# McFadden's R squared
aux.null <- multinom(cluster.up ~ 1, data = data)
r2 <- 1-logLik(aux)/logLik(aux.null)

n.obs <- dim(aux$fitted.values)[1]

stargazer(aux, 
          type = "html",
          #type = "text",
          nobs = T,
          digits = 3,
          covariate.labels=c(#"pop. 16-64, 2018",
                             "pop, 2018",
                             #"pop. densuty, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "South of the UK",
                             "% of managerial jobs, 2020",
                             "% of tech jobs, 2020",
                             "% of skilled trade jobs, 2020",
                             "% of professional jobs, 2020",
                             "% of administrative jobs, 2020",
                             "% of leisure jobs, 2020",
                             "% of machine operation jobs, 2020",
                             "earnings, 2019",
                             "n. business est. per hab., 2019",
                             "% of NVQ4+",
                             "n. of AM broadband tests per hab., 2019",
                             "% of Virgin Media connections"),
          add.lines = list(c("McFadden's R squared",
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3)
                             , round(r2[1],3), round(r2[1],3)),
                           (c("N",
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs
                            , n.obs, n.obs))))

@@

aux <- multinom(cluster.tests ~ 
                  #pop16_64 + # non sign, while pop is
                  pop +
                  #pop.dens + 
                  job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                  distMet + distLondon + south + nvq4 +
                  managers + tech + skilled + prof + admin + caring + plant +
                  earnings + I(total.busi/pop) +
                  I(LAD.tests.am20/pop) + # non sensitive to addition of other tests pm
                  virgin
                , data = data, 
                trace = F) # to avoid messages

# McFadden's R squared
aux.null <- multinom(cluster.tests ~ 1, data = data)
r2 <- 1-logLik(aux)/logLik(aux.null)

n.obs <- dim(aux$fitted.values)[1]

stargazer(aux, 
          type = "html",
          #type = "text",
          digits = 3,
          covariate.labels=c(#"pop. 16-64, 2018",
                             "pop, 2018",
                             #"pop. densuty, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "South of the UK",
                             "% of managerial jobs, 2020",
                             "% of tech jobs, 2020",
                             "% of skilled trade jobs, 2020",
                             "% of professional jobs, 2020",
                             "% of administrative jobs, 2020",
                             "% of leisure jobs, 2020",
                             "% of machine operation jobs, 2020",
                             "earnings, 2019",
                             "n. business est. per hab., 2019",
                             "% of NVQ4+",
                             "n. of AM broadband tests per hab., 2019",
                             "% of Virgin Media connections"),
          add.lines = list(c("McFadden's R squared",
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3)),
                           (c("N",
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs))))

@@

aux <- multinom(cluster.down ~ 
                  #pop16_64 + # non sign, while pop is
                  pop +
                  #pop.dens + 
                  job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                  distMet + distLondon + south +
                  managers + tech + skilled + prof + admin + caring + plant +
                  earnings + I(total.busi/pop) + nvq4 +
                  I(LAD.tests.am20/pop) + # non sensitive to addition of other tests pm
                  virgin
                , data = data, 
                trace = F) # to avoid messages

# McFadden's R squared
aux.null <- multinom(cluster.down ~ 1, data = data)
r2 <- 1-logLik(aux)/logLik(aux.null)

n.obs <- dim(aux$fitted.values)[1]

stargazer(aux, 
          type = "html",
          #type = "text",
          digits = 3,
          covariate.labels=c(#"pop. 16-64, 2018",
                             "pop, 2018",
                             #"pop. densuty, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "South of the UK",
                             "% of managerial jobs, 2020",
                             "% of tech jobs, 2020",
                             "% of skilled trade jobs, 2020",
                             "% of professional jobs, 2020",
                             "% of administrative jobs, 2020",
                             "% of leisure jobs, 2020",
                             "% of machine operation jobs, 2020",
                             "earnings, 2019",
                             "n. business est. per hab., 2019",
                             "% of NVQ4+",
                             "n. of AM broadband tests per hab., 2019",
                             "% of Virgin Media connections"),
          add.lines = list(c("McFadden's R squared",
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3)),
                           (c("N",
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs))))

@@

>>>>

aux.up <- multinom(cluster.up ~ 
                  #pop16_64 + # non sign, while pop is
                  pop +
                  #pop.dens + 
                  job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                  distMet + distLondon + south +
                  managers + tech + skilled + prof + admin + caring + plant +
                  earnings + I(total.busi/pop) + nvq4 +
                  I(LAD.tests.am20/pop) + # non sensitive to addition of other tests pm
                  virgin
                , data = data, 
                trace = F) # to avoid messages

# McFadden's R squared
aux.up.null <- multinom(cluster.up ~ 1, data = data)
r2.up <- 1-logLik(aux.up)/logLik(aux.up.null)

n.obs <- dim(aux.up$fitted.values)[1]

stargazer(aux.up, 
          #type = "html",
          type = "text",
          nobs = T,
          digits = 3,
          covariate.labels=c(#"pop. 16-64, 2018",
                             "pop, 2018",
                             #"pop. densuty, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "South of the UK",
                             "% of managerial jobs, 2020",
                             "% of tech jobs, 2020",
                             "% of skilled trade jobs, 2020",
                             "% of professional jobs, 2020",
                             "% of administrative jobs, 2020",
                             "% of leisure jobs, 2020",
                             "% of machine operation jobs, 2020",
                             "earnings, 2019",
                             "n. business est. per hab., 2019",
                             "% of NVQ4+",
                             "n. of AM broadband tests per hab., 2020",
                             "% of Virgin Media connections"),
          add.lines = list(c("McFadden's R squared",
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3),
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3),
                             round(r2.up[1],3), round(r2.up[1],3), round(r2.up[1],3)
                             , round(r2.up[1],3), round(r2.up[1],3)),
                           (c("N",
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs
                            , n.obs, n.obs))))

@@

aux.tests <- multinom(cluster.tests ~ 
                  #pop16_64 + # non sign, while pop is
                  pop +
                  #pop.dens + 
                  job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                  distMet + distLondon + south + nvq4 +
                  managers + tech + skilled + prof + admin + caring + plant +
                  earnings + I(total.busi/pop) +
                  I(LAD.tests.am20/pop) + # non sensitive to addition of other tests pm
                  virgin
                , data = data, 
                trace = F) # to avoid messages

# McFadden's R squared
aux.tests.null <- multinom(cluster.tests ~ 1, data = data)
r2.tests <- 1-logLik(aux.tests)/logLik(aux.tests.null)

n.obs <- dim(aux.tests$fitted.values)[1]

stargazer(aux.tests, 
          type = "html",
          #type = "text",
          digits = 3,
          covariate.labels=c(#"pop. 16-64, 2018",
                             "pop, 2018",
                             #"pop. densuty, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "South of the UK",
                             "% of managerial jobs, 2020",
                             "% of tech jobs, 2020",
                             "% of skilled trade jobs, 2020",
                             "% of professional jobs, 2020",
                             "% of administrative jobs, 2020",
                             "% of leisure jobs, 2020",
                             "% of machine operation jobs, 2020",
                             "earnings, 2019",
                             "n. business est. per hab., 2019",
                             "% of NVQ4+",
                             "n. of AM broadband tests per hab., 2020",
                             "% of Virgin Media connections"),
          add.lines = list(c("McFadden's R squared",
                             round(r2.tests[1],3), round(r2.tests[1],3), round(r2.tests[1],3),
                             round(r2.tests[1],3), round(r2.tests[1],3), round(r2.tests[1],3)),
                           (c("N",
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs))))

@@

aux.down <- multinom(cluster.down ~ 
                  #pop16_64 + # non sign, while pop is
                  pop +
                  #pop.dens + 
                  job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                  distMet + distLondon + south +
                  managers + tech + skilled + prof + admin + caring + plant +
                  earnings + I(total.busi/pop) + nvq4 +
                  I(LAD.tests.am20/pop) + # non sensitive to addition of other tests pm
                  virgin
                , data = data, 
                trace = F) # to avoid messages

# McFadden's R squared
aux.down.null <- multinom(cluster.down ~ 1, data = data)
r2.down <- 1-logLik(aux.down)/logLik(aux.down.null)

n.obs <- dim(aux.down$fitted.values)[1]

stargazer(aux.down, 
          type = "html",
          #type = "text",
          digits = 3,
          covariate.labels=c(#"pop. 16-64, 2018",
                             "pop, 2018",
                             #"pop. densuty, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "South of the UK",
                             "% of managerial jobs, 2020",
                             "% of tech jobs, 2020",
                             "% of skilled trade jobs, 2020",
                             "% of professional jobs, 2020",
                             "% of administrative jobs, 2020",
                             "% of leisure jobs, 2020",
                             "% of machine operation jobs, 2020",
                             "earnings, 2019",
                             "n. business est. per hab., 2019",
                             "% of NVQ4+",
                             "n. of AM broadband tests per hab., 2020",
                             "% of Virgin Media connections"),
          add.lines = list(c("McFadden's R squared",
                             round(r2.down[1],3), round(r2.down[1],3), round(r2.down[1],3),
                             round(r2.down[1],3), round(r2.down[1],3), round(r2.down[1],3),
                             round(r2.down[1],3), round(r2.down[1],3), round(r2.down[1],3),
                             round(r2.down[1],3), round(r2.down[1],3), round(r2.down[1],3),
                             round(r2.down[1],3), round(r2.down[1],3), round(r2.down[1],3),
                             round(r2.down[1],3), round(r2.down[1],3), round(r2.down[1],3),
                             round(r2.down[1],3)),
                           (c("N",
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs))))

@@

```{r}
path.out <- paste0(path, "/data/temp/LAs_Clusters.RData")
save.image(path.out)
```

### 2021-09-22 src/old/online_appendix_old.Rmd
tidy up

---
title: "Online Appendix"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    social: menu
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../paper/v2_taylor_francis/")
  })
---

@@

# save clusters file
path.clusters <- paste(path, "/data/temp/clusters_nodiff_9.csv", sep = "")
clusters.nodiff <- read_csv(path.clusters)
```

Column 
-----------------------------------------------------------------------

### LAD, Upload speed clusters, 2020

```{r, echo=FALSE, warning=FALSE, message = FALSE, error=FALSE, fig.height=10}
#out.width='100%'

@@

# create the text to tooltip
la.f <- merge(la.f, for.tip.mean.up.am, by.x = "id", by.y = "LAD19NM", all.x=T)
#sapply(la.f, function(x) sum(is.na(x)))
#No am data points for Isles of Scilly
la.f$tip <- paste0(la.f$id, "<br>",
                   "Upload AM speed: ", round(la.f$mean.up.am), " Kbps", "<br>",
                   "Rank: ", la.f$rank)
la.f <- la.f[order(la.f$order),] # if i don't order merge.nuts.f loses order and the map has gaps

@@

  guides(fill=guide_legend(title="Cluster")) +
  theme_map()
#   theme(panel.border = element_blank(), panel.grid.major = element_blank(),
# panel.grid.minor = element_blank())

@@

Column
-----------------------------------------------------------------------

### LAD mean AM upload speeds and ranking

```{r, echo=FALSE, warning=FALSE, message = FALSE, error=FALSE,fig.height=10}
for.tip.mean.up.am <- merge(for.tip.mean.up.am, clusters.nodiff, 
                            by.x = "LAD19NM", by.y = "LAD", all.x = T)

for.tip.mean.up.am %>% 
  select(-cluster.down, -cluster.tests) %>% 
  arrange(rank) %>% 
  kable(digits = 0,
        format.args = list(big.mark = ","),
        col.names = c("Local Authority",
                      "Mean AM upload sped",
                      "Rank",
                      "Cluster")) %>% 
  kable_styling("striped", full_width = F) %>% 
  scroll_box() #width = "500px", height = "400px"
```

### Description

- Cluster 2:

...

>>>>

---
title: "Online Appendix"
author: ""
output: html_document
header-includes:
- \usepackage{multirow}
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../paper/v2_taylor_francis/")
  })
---

@@

# save clusters file
path.clusters <- paste(path, "/data/temp/clusters_nodiff_9.csv", sep = "")
clusters.nodiff <- read_csv(path.clusters)
```
## Local Authority Districts

- Cluster 2: 
...

<br>
```{r, echo=FALSE, warning=FALSE, message = FALSE, error=FALSE,fig.height=10}

@@

# create the text to tooltip
la.f <- merge(la.f, for.tip.mean.up.am, by.x = "id", by.y = "LAD19NM", all.x=T)
#sapply(la.f, function(x) sum(is.na(x)))
#No am data points for Isles of Scilly
la.f$tip <- paste0(la.f$id, "<br>",
                   "Upload am: ", round(la.f$mean.up.am), " Kbps", "<br>",
                   "Rank: ", la.f$rank)
la.f <- la.f[order(la.f$order),] # if i don't order merge.nuts.f loses order and the map has gaps

@@

  guides(fill=guide_legend(title="Clusters")) +
  theme_map()
#   theme(panel.border = element_blank(), panel.grid.major = element_blank(),
# panel.grid.minor = element_blank())

@@

```{r, echo=FALSE, warning=FALSE, message = FALSE, error=FALSE,fig.height=10}
for.tip.mean.up.am %>% 
    arrange(rank) %>% 
  kable(digits = 0,
        format.args = list(big.mark = ",")) %>% 
  kable_styling("striped", full_width = F) %>% 
  scroll_box(width = "500px", height = "400px")

```

### 2021-09-22 src/old/timeseries_plots0916.Rmd
tidy up

## Sub-daily timeseries

@@

# create sub daily blocks
bb2020sp$block[bb2020sp$hour>=0 & bb2020sp$hour<8] <- 1
bb2020sp$block[bb2020sp$hour>=8 & bb2020sp$hour<16] <- 2
bb2020sp$block[bb2020sp$hour>=16 & bb2020sp$hour<24] <- 3

#bb2020sp$date.block <- paste(bb2020sp$date, bb2020sp$date.block, sep = "_")
# I use block as hour for the ts_wide()
bb2020sp$date.block = ymd_h(paste(bb2020sp$date, bb2020sp$block))

@@

```{r include=TRUE, echo=FALSE, results= 'markup', message=FALSE, warning = FALSE, fig.height=600, fig.width=14}
ts.down <- bb2020sp %>%
  group_by(date.block,LAD19NM) %>%
  summarise(mean.down = mean(speeddown))#, mean.down = mean(speeddown), n.tests = n())
sapply(ts.down, function(x) sum(is.na(x)))

@@

mean.down.uk <- ts.down %>%
  group_by(date.block) %>%
  summarise(mean.down.uk = mean(mean.down))#, mean.down = mean(speeddown), n.tests = n())

@@

ggplot(subset(ts.down,date.block > start.date), aes(x=as.POSIXct(date.block), y=mean.down, group = LAD19NM, colour = "red")) +
  geom_line() + guides(colour=FALSE) + ggtitle("Download speeds") + #xlab("") +
  ylab("download speed") +
  scale_y_continuous(labels = scales::comma) +
  scale_x_datetime(date_breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~LAD19NM, ncol = 2) +
  geom_line(data = subset(mean.down.uk,date.block > start.date), aes(x=as.POSIXct(date.block), y=mean.down.uk, group = 1), colour="green") #

@@

```{r include=TRUE, echo=FALSE, results= 'markup', message=FALSE, warning = FALSE, fig.height=600, fig.width=14}
ts.up <- bb2020sp %>%
  group_by(date.block,LAD19NM) %>%
  summarise(mean.up = mean(speedup))
sapply(ts.up, function(x) sum(is.na(x)))

@@

mean.up.uk <- ts.up %>%
  group_by(date.block) %>%
  summarise(mean.up.uk = mean(mean.up))

@@

ggplot(subset(ts.up,date.block > start.date), aes(x=as.POSIXct(date.block), y=mean.up, group = LAD19NM, colour = "red")) +
  geom_line() + guides(colour=FALSE) + ggtitle("Upload speeds") + #xlab("") +
  ylab("upload speed") +
  scale_y_continuous(labels = scales::comma) +
  scale_x_datetime(date_breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~LAD19NM, ncol = 2) +
  geom_line(data = subset(mean.up.uk,date.block > start.date), aes(x=as.POSIXct(date.block), y=mean.up.uk, group = 1), colour="green") #

@@

```{r include=TRUE, echo=FALSE, results= 'markup', message=FALSE, warning = FALSE, fig.height=600, fig.width=14}
ts.tests <- bb2020sp %>%
  group_by(date.block,LAD19NM) %>%
  summarise(n.tests = n())
sapply(ts.tests, function(x) sum(is.na(x)))

@@

mean.tests.uk <- ts.tests %>%
  group_by(date.block) %>%
  summarise(mean.tests.uk = mean(n.tests))

@@

ggplot(subset(ts.tests,date.block > start.date), aes(x=as.POSIXct(date.block), y=n.tests, group = LAD19NM, colour = "red")) +
  geom_line() + guides(colour=FALSE) + ggtitle("N. of tests") + #xlab("") +
  ylab("tests") +
  scale_y_continuous(labels = scales::comma) +
  scale_x_datetime(date_breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~LAD19NM, ncol = 2, scales = "free_y") +
  geom_line(data = subset(mean.tests.uk,date.block > start.date), aes(x=as.POSIXct(date.block), y=mean.tests.uk, group = 1), colour="green") #.uk

@@

ts.down.diff <- ts.down
ts.down.diff$date.block.lag1y <- ts.down.diff$date.block - years(1)
ts.down.diff <- merge(ts.down.diff,ts.down.diff, by.x = c("date.block.lag1y", "LAD19NM"), by.y = c("date.block","LAD19NM"), all = F)

ts.down.diff <- ts.down.diff %>%
  rename(mean.down2019 = mean.down.y, mean.down2020 = mean.down.x) %>%
  select(-date.block.lag1y.y)

@@

mean.down.diff.uk <- ts.down.diff %>%
  group_by(date.block) %>%
  summarise(mean.down.diff.uk = mean(diff))#, mean.down = mean(speeddown), n.tests = n())

@@

ggplot(subset(ts.down.diff,date.block > start.date), aes(x=as.POSIXct(date.block), y=diff, group = LAD19NM, colour = "red")) +
  geom_line() + guides(colour=FALSE) + ggtitle("Diff. in download speeds") + #xlab("") +
  ylab("diff. in download speed") +
  scale_y_continuous(labels = scales::comma) +
  scale_x_datetime(date_breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~LAD19NM, ncol = 2) +
  geom_line(data = subset(mean.down.uk,date.block > start.date), aes(x=as.POSIXct(date.block), y=mean.down.uk, group = 1), colour="green") #
```

@@

ts.up.diff <- ts.up
ts.up.diff$date.block.lag1y <- ts.up.diff$date.block - years(1)
ts.up.diff <- merge(ts.up.diff,ts.up.diff, by.x = c("date.block.lag1y", "LAD19NM"), by.y = c("date.block","LAD19NM"), all = F)

ts.up.diff <- ts.up.diff %>%
  rename(mean.up2019 = mean.up.y, mean.up2020 = mean.up.x) %>%
  select(-date.block.lag1y.y)

@@

mean.up.diff.uk <- ts.up.diff %>%
  group_by(date.block) %>%
  summarise(mean.up.diff.uk = mean(diff))#, mean.up = mean(speedup), n.tests = n())

@@

ggplot(subset(ts.up.diff,date.block > start.date), aes(x=as.POSIXct(date.block), y=diff, group = LAD19NM, colour = "red")) +
  geom_line() + guides(colour=FALSE) + ggtitle("Diff. in upload speeds") + #xlab("") +
  ylab("diff. in upload speed") +
  scale_y_continuous(labels = scales::comma) +
  scale_x_datetime(date_breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~LAD19NM, ncol = 2) +
  geom_line(data = subset(mean.up.diff.uk,date.block > start.date), aes(x=as.POSIXct(date.block), y=mean.up.diff.uk, group = 1), colour="green") #
```

@@

```{r include=TRUE, echo=FALSE, results= 'markup', message=FALSE, warning = FALSE, fig.height=600, fig.width=14}
ts.tests.diff <- ts.tests
ts.tests.diff$date.block.lag1y <- ts.tests.diff$date.block - years(1)
ts.tests.diff <- merge(ts.tests.diff,ts.tests.diff, by.x = c("date.block.lag1y", "LAD19NM"), by.y = c("date.block","LAD19NM"), all = F)

ts.tests.diff <- ts.tests.diff %>%
  rename(n.tests2019 = n.tests.y, n.tests2020 = n.tests.x) %>%
  select(-date.block.lag1y.y)

@@

mean.tests.diff.uk <- ts.tests.diff %>%
  group_by(date.block) %>%
  summarise(mean.tests.diff.uk = mean(diff))

@@

ggplot(subset(ts.tests.diff,date.block > start.date), aes(x=as.POSIXct(date.block), y=diff, group = LAD19NM, colour = "red")) +
  geom_line() + guides(colour=FALSE) + ggtitle("Diff. in speed tests") + #xlab("") +
  ylab("diff. in speed tests") +
  scale_y_continuous(labels = scales::comma) +
  scale_x_datetime(date_breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~LAD19NM, ncol = 2) +
  geom_line(data = subset(mean.tests.diff.uk,date.block > start.date), aes(x=as.POSIXct(date.block), y=mean.tests.diff.uk, group = 1), colour="green") #
```

>>>>

## Keep working hours

@@

# keep working hours
bb2020sp <- bb2020sp[bb2020sp$hour>=9 & bb2020sp$hour<17,]

# drop w/e
bb2020sp <- bb2020sp %>%
  filter(bb2020sp$weekday!="Sat" & bb2020sp$weekday!="Sun")

@@

```{r include=TRUE, echo=FALSE, results= 'markup', message=FALSE, warning = FALSE, fig.height=600, fig.width=14}
ts.down <- bb2020sp %>%
  group_by(date,LAD19NM) %>%
  summarise(mean.down = mean(speeddown))#, mean.down = mean(speeddown), n.tests = n())
sapply(ts.down, function(x) sum(is.na(x)))

@@

mean.down.uk <- ts.down %>%
  group_by(date) %>%
  summarise(mean.down.uk = mean(mean.down))#, mean.down = mean(speeddown), n.tests = n())

@@

ggplot(subset(ts.down,date > start.date), aes(x=as.POSIXct(date), y=mean.down, group = LAD19NM, colour = "red")) +
  geom_line() + guides(colour=FALSE) + ggtitle("Download speeds") + #xlab("") +
  ylab("download speed") +
  scale_y_continuous(labels = scales::comma) +
  scale_x_datetime(date_breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~LAD19NM, ncol = 2) +
  geom_line(data = subset(mean.down.uk,date > start.date), aes(x=as.POSIXct(date), y=mean.down.uk, group = 1), colour="green") #

@@

```{r include=TRUE, echo=FALSE, results= 'markup', message=FALSE, warning = FALSE, fig.height=600, fig.width=14}
ts.up <- bb2020sp %>%
  group_by(date,LAD19NM) %>%
  summarise(mean.up = mean(speedup))
sapply(ts.up, function(x) sum(is.na(x)))

@@

mean.up.uk <- ts.up %>%
  group_by(date) %>%
  summarise(mean.up.uk = mean(mean.up))

@@

ggplot(subset(ts.up,date > start.date), aes(x=as.POSIXct(date), y=mean.up, group = LAD19NM, colour = "red")) +
  geom_line() + guides(colour=FALSE) + ggtitle("Upload speeds") + #xlab("") +
  ylab("upload speed") +
  scale_y_continuous(labels = scales::comma) +
  scale_x_datetime(date_breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~LAD19NM, ncol = 2) +
  geom_line(data = subset(mean.up.uk,date > start.date), aes(x=as.POSIXct(date), y=mean.up.uk, group = 1), colour="green") #

@@

```{r include=TRUE, echo=FALSE, results= 'markup', message=FALSE, warning = FALSE, fig.height=600, fig.width=14}
ts.tests <- bb2020sp %>%
  group_by(date,LAD19NM) %>%
  summarise(n.tests = n())
sapply(ts.tests, function(x) sum(is.na(x)))

@@

mean.tests.uk <- ts.tests %>%
  group_by(date) %>%
  summarise(mean.tests.uk = mean(n.tests))

@@

ggplot(subset(ts.tests,date > start.date), aes(x=as.POSIXct(date), y=n.tests, group = LAD19NM, colour = "red")) +
  geom_line() + guides(colour=FALSE) + ggtitle("N. of tests") + #xlab("") +
  ylab("tests") +
  scale_y_continuous(labels = scales::comma) +
  scale_x_datetime(date_breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~LAD19NM, ncol = 2, scales = "free_y") +
  geom_line(data = subset(mean.tests.uk,date > start.date), aes(x=as.POSIXct(date), y=mean.tests.uk, group = 1), colour="green") #.uk

@@

ts.down.diff <- ts.down
ts.down.diff$date.lag1y <- ts.down.diff$date - years(1)
ts.down.diff <- merge(ts.down.diff,ts.down.diff, by.x = c("date.lag1y", "LAD19NM"), by.y = c("date","LAD19NM"), all = F)

ts.down.diff <- ts.down.diff %>%
  rename(mean.down2019 = mean.down.y, mean.down2020 = mean.down.x) %>%
  select(-date.lag1y.y)

@@

mean.down.diff.uk <- ts.down.diff %>%
  group_by(date) %>%
  summarise(mean.down.diff.uk = mean(diff))#, mean.down = mean(speeddown), n.tests = n())

@@

ggplot(subset(ts.down.diff,date > start.date), aes(x=as.POSIXct(date), y=diff, group = LAD19NM, colour = "red")) +
  geom_line() + guides(colour=FALSE) + ggtitle("Diff. in download speeds") + #xlab("") +
  ylab("diff. in download speed") +
  scale_y_continuous(labels = scales::comma) +
  scale_x_datetime(date_breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~LAD19NM, ncol = 2) +
  geom_line(data = subset(mean.down.uk,date > start.date), aes(x=as.POSIXct(date), y=mean.down.uk, group = 1), colour="green") #
```

@@

ts.up.diff <- ts.up
ts.up.diff$date.lag1y <- ts.up.diff$date - years(1)
ts.up.diff <- merge(ts.up.diff,ts.up.diff, by.x = c("date.lag1y", "LAD19NM"), by.y = c("date","LAD19NM"), all = F)

ts.up.diff <- ts.up.diff %>%
  rename(mean.up2019 = mean.up.y, mean.up2020 = mean.up.x) %>%
  select(-date.lag1y.y)

@@

mean.up.diff.uk <- ts.up.diff %>%
  group_by(date) %>%
  summarise(mean.up.diff.uk = mean(diff))#, mean.up = mean(speedup), n.tests = n())

@@

ggplot(subset(ts.up.diff,date > start.date), aes(x=as.POSIXct(date), y=diff, group = LAD19NM, colour = "red")) +
  geom_line() + guides(colour=FALSE) + ggtitle("Diff. in upload speeds") + #xlab("") +
  ylab("diff. in upload speed") +
  scale_y_continuous(labels = scales::comma) +
  scale_x_datetime(date_breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~LAD19NM, ncol = 2) +
  geom_line(data = subset(mean.up.diff.uk,date > start.date), aes(x=as.POSIXct(date), y=mean.up.diff.uk, group = 1), colour="green") #
```

@@

```{r include=TRUE, echo=FALSE, results= 'markup', message=FALSE, warning = FALSE, fig.height=600, fig.width=14}
ts.tests.diff <- ts.tests
ts.tests.diff$date.lag1y <- ts.tests.diff$date - years(1)
ts.tests.diff <- merge(ts.tests.diff,ts.tests.diff, by.x = c("date.lag1y", "LAD19NM"), by.y = c("date","LAD19NM"), all = F)

ts.tests.diff <- ts.tests.diff %>%
  rename(n.tests2019 = n.tests.y, n.tests2020 = n.tests.x) %>%
  select(-date.lag1y.y)

@@

mean.tests.diff.uk <- ts.tests.diff %>%
  group_by(date) %>%
  summarise(mean.tests.diff.uk = mean(diff))

@@

ggplot(subset(ts.tests.diff,date > start.date), aes(x=as.POSIXct(date), y=diff, group = LAD19NM, colour = "red")) +
  geom_line() + guides(colour=FALSE) + ggtitle("Diff. in speed tests") + #xlab("") +
  ylab("diff. in speed tests") +
  scale_y_continuous(labels = scales::comma) +
  scale_x_datetime(date_breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~LAD19NM, ncol = 2) +
  geom_line(data = subset(mean.tests.diff.uk,date > start.date), aes(x=as.POSIXct(date), y=mean.tests.diff.uk, group = 1), colour="green") #
```
